--- 
title: "Análisis de series de tiempo - IPC en Colombia"
author: "Isabel Fernandez, Luis Guillermo cortés"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
documentclass: book
bibliography:
- book.bib
- packages.bib
description: |
  "Se presenta este libro como trabajo principal de Análisis de series de tiempo."
link-citations: true
github-repo: https://github.com/LGuillermoCortes/Bookdown_Series.git
site: bookdown::bookdown_site
---


Propuesta:
La propuesta se enfocará en el análisis de la serie de tiempo del Índice de Precios al Consumidor (IPC)  de Colombia, suministrada por el DANE, la cual contiene datos desde el 1 de julio de 1955 hasta el 1 de octubre de 2024 con una frecuencia mensual. El IPC es un indicador clave para medir la variación de los precios de una canasta de bienes y servicios en el tiempo, y es fundamental para el análisis económico, la toma de decisiones políticas y la planificación financiera.

Fuente:  
DANE -  https://sitios.dane.gov.co/ipc/visorIPC/#!/

Herramientas utilizadas:
Para la publicación del libro Bookdown, se utilizó R Studio, en el cual se cargaron los datos a trabajar, y posteriormente se cargan a la plataforma GitHub.

## Preview book


```{r eval=FALSE}
bookdown::serve_book()
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Hello bookdown 

All chapters start with a first-level heading followed by your chapter title, like the line above. There should be only one first-level heading (`#`) per .Rmd file.

## A section

All chapter sections start with a second-level (`##`) or higher heading followed by your section title, like the sections above and below here. You can have as many as you want within a chapter.

### An unnumbered section {-}

Chapters and sections are numbered by default. To un-number a heading, add a `{.unnumbered}` or the shorter `{-}` at the end of the heading, like in this section.

<!--chapter:end:01-intro.Rmd-->


# Cross-references {#cross}

Placeholder


## Chapters and sub-chapters
## Captioned figures and tables

<!--chapter:end:02-cross-refs.Rmd-->

# Parts

You can add parts to organize one or more book chapters together. Parts can be inserted at the top of an .Rmd file, before the first-level chapter heading in that same file. 

Add a numbered part: `# (PART) Act one {-}` (followed by `# A chapter`)

Add an unnumbered part: `# (PART\*) Act one {-}` (followed by `# A chapter`)

Add an appendix as a special kind of un-numbered part: `# (APPENDIX) Other stuff {-}` (followed by `# A chapter`). Chapters in an appendix are prepended with letters instead of numbers.




<!--chapter:end:03-parts.Rmd-->

# Footnotes and citations 

## Footnotes

Footnotes are put inside the square brackets after a caret `^[]`. Like this one ^[This is a footnote.]. 

## Citations

Reference items in your bibliography file(s) using `@key`.

For example, we are using the **bookdown** package [@R-bookdown] (check out the last code chunk in index.Rmd to see how this citation key was added) in this sample book, which was built on top of R Markdown and **knitr** [@xie2015] (this citation was added manually in an external file book.bib). 
Note that the `.bib` files need to be listed in the index.Rmd with the YAML `bibliography` key.


The RStudio Visual Markdown Editor can also make it easier to insert citations: <https://rstudio.github.io/visual-markdown-editing/#/citations>

<!--chapter:end:04-citations.Rmd-->


# Blocks

Placeholder


## Equations
## Theorems and proofs
## Callout blocks

<!--chapter:end:05-blocks.Rmd-->


# Sharing your book

Placeholder


## Publishing
## 404 pages
## Metadata for sharing

<!--chapter:end:06-share.Rmd-->

`r if (knitr::is_html_output()) '
# References {-}
'`

<!--chapter:end:07-references.Rmd-->

